---
title: "Data Analysis and Visualization - Assignment 2"
author: "Ma Jingchun, 2020111235"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

**1**
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(readxl)
library(tibble)
library(dplyr)
library(lubridate)
```

```{r, include=T, echo=T}
######### Please write your R code in this chunk #########
### Solution to Q1
d <- as_tibble(read_excel("dataset-cac-ma.xlsx",1))
head(d)
```
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip


**2**
```{r, include=T, echo=T}
######### Please write your R code in this chunk #########
### Solution to Q2
# type
str(d)
# descriptive statistics
summary(d)
```
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip


**3**
```{r, include=T, echo=T}
######### Please write your R code in this chunk #########
### Solution to Q3
d1 <- select(d, list_price, cost)[5:10,]
d1
```
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip

**4**

```{r, include=T, echo=T}
######### Please write your R code in this chunk #########
### Solution to Q4
d2 <- filter(d, customer_number == 175749)
d2
d3 <- filter(d, region == "Midwest")
d3
```
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip


**5**

```{r, include=T, echo=T}
######### Please write your R code in this chunk #########
### Solution to Q5
# region 不同取值个数
length(unique(d$region))
# 修改前，有错误数据
aggregate(d$item,by=list(region=d$region),length)
d[d$region=="Centrall","region"] <- "Central"
d[d$region=="Soouth","region"] <- "South"
# 修改后
length(unique(d$region))
aggregate(d$item,by=list(region=d$region),length)
```
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip

**6**

+ sales revenue = quantity sold * list_price

+ variable cost = quantity sold * cost

+ contribution margin = (sales revenue - variable cost) / sales revenue
```{r, include=T, echo=T}
######### Please write your R code in this chunk #########
### Solution to Q6
d <- mutate(d,
  "sales revenue" = quantity_sold * list_price,
  "variable cost" = quantity_sold * cost,
  "contribution margin" = (`sales revenue` - `variable cost`) / `sales revenue`
  )
```
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip

**7**
```{r}
######### Please write your R code in this chunk #########
### Solution to Q7
d <- mutate(d,
  year_quarter = paste(year(date_of_sale),quarter(date_of_sale),sep="_")
  )
d %>%
  group_by( region, year_quarter) %>%
  summarise( ave_contribution_margin=mean(`contribution margin`, na.rm = TRUE))
```
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip

**8**
```{r}
######### Please write your R code in this chunk #########
### Solution to Q8
d <- mutate(d,
  year = year(date_of_sale)
  )
d %>%
  group_by( year,region) %>%
  summarise( ave_contribution_margin=mean(`contribution margin`, na.rm = TRUE)) %>%
  arrange( desc(ave_contribution_margin),.by_group = TRUE) %>%
  filter(row_number() <= 3)


```
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip

**9**
```{r}
######### Please write your R code in this chunk #########
### Solution to Q9
d %>%
  group_by( year, collection) %>%
  summarise( profit = sum(`sales revenue` - `variable cost`, na.rm = TRUE)) %>%
  arrange( desc(profit), .by_group = TRUE) %>%
  filter(row_number() <= 3)
  
```
note: profit = sales revenue - variable cost
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip

**10 **
```{r}
######### Please write your R code in this chunk #########
### Solution to Q10
d %>%
  filter( year == 2018) %>%
  group_by( brand, collection) %>%
  summarise( profit = sum(`sales revenue` - `variable cost`, na.rm = TRUE)) %>%
  arrange( desc(profit), .by_group = TRUE) %>%
  filter(row_number() <= 1)
```

